\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.1in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-3pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.12in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------

\begin{document}

\begin{center}
    \textbf{\Huge \scshape ARYAN KUMAR} \\ \vspace{2pt}
    \small 
    \faPhone\ +91 99721 19604 $|$
    \href{mailto:aryantk4848@gmail.com}{aryantk4848@gmail.com} $|$
    \href{https://linkedin.com/in/aryan-tk/}{linkedin.com/in/aryan-tk} $|$
    \href{https://github.com/aryankumar4848}{github.com/aryankumar4848}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
\resumeItem{
Final-year Computer Science undergraduate with strong foundations in Data Structures, Operating Systems, and Networking. Experienced in designing concurrent, ACID-compliant backend systems and containerized microservices using \textbf{Java, Spring Boot, PostgreSQL, and Docker}.
}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {M. S. Ramaiah Institute of Technology}{Bangalore, India}
    {B.E. in Computer Science Engineering (CGPA: 8.68)}{2022 - 2026}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Full Stack Developer Intern}{Bangalore, India}
    {Ramaiah Institute of Technology}{}
    \resumeItemListStart
    \resumeItem{Engineered a MERN-based booking system by implementing JWT-based RBAC and atomic slot validation logic, eliminating 100\% double-booking across 5,000+ simulated reservations.}
    \resumeItem{Improved database performance by introducing indexed MongoDB queries and benchmarking execution paths, increasing retrieval speed by 3x over 5k+ records.}
    \resumeItem{Accelerated release cycles by automating CI pipelines using GitHub Actions, reducing deployment time by 60\% (20 min → 8 min).}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
  {\textbf{AgriConnect: AI-Powered Agricultural Marketplace \& Advisory Platform}
  \href{https://github.com/aryankumar4848/AgriConnect}{\faIcon{external-link-alt}}
  $|$ \emph{React, Node.js/Express, MongoDB, Razorpay, Docker, Prometheus, Filebeat}}{}
  \resumeItemListStart
    \resumeItem{Developed full-stack MERN marketplace supporting 40+ crop/fertilizer products (3000+ SKUs across seeds, tools), with image-optimized product catalog (60+ high-res assets).}
    \resumeItem{Integrated Razorpay payment links with signature verification, enabling secure checkout flows and mock testing mode for 100\% transaction idempotency.}
    \resumeItem{Containerized client/server with Docker Compose + monitoring stack (Prometheus metrics endpoint, Filebeat/Logstash logging), supporting production-grade observability.}
    \resumeItem{Built feature-complete modules: crop suggestion AI, farmer dashboard, admin portal, real-time discussions (timestamped messaging), and cart management with MongoDB models.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItem{
\textbf{Languages:} Java, Python, JavaScript, SQL \\
\textbf{Backend:} Spring Boot, Spring Cloud, Node.js, REST APIs, Hibernate \\
\textbf{Databases:} PostgreSQL, MySQL, MongoDB \\
\textbf{DevOps:} Docker, Git, GitHub Actions, Jenkins (basic) \\
\textbf{Core Concepts:} DSA, OOPS, Concurrency, Microservices, Distributed Systems \\
\textbf{OS \& Networking:} Process Management, Synchronization, TCP/IP, HTTP/HTTPS
}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS AND ACHIEVEMENTS-----------
\section{Certifications And Achievements}
\resumeSubHeadingListStart

\resumeItem{
\textbf{Research Paper Accepted (IEEE I3CTCON 2026)} — \textit{MBTI Cognitive Chatbot: Personality-Aware Conversational AI Architecture}. 
Accepted for presentation at the IEEE International Conference for Convergence in Computing Technology (I3CTCON), Pune, India. Publication in IEEE Xplore pending.
}

\resumeItem{
\textbf{Azure AZ-900} — In Progress
}

\resumeItem{
\textbf{Solved 200+ DSA Problems} across LeetCode and GeeksforGeeks
}

\resumeSubHeadingListEnd

\end{document}

