\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.1in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-3pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.12in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------

\begin{document}

\begin{center}
    \textbf{\Huge \scshape ARYAN KUMAR} \\ \vspace{2pt}
    \small 
    \faPhone\ +91 99721 19604 $|$
    \href{mailto:aryantk4848@gmail.com}{aryantk4848@gmail.com} $|$
    \href{https://linkedin.com/in/aryan-tk/}{linkedin.com/in/aryan-tk} $|$
    \href{https://github.com/aryankumar4848}{github.com/aryankumar4848}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
\resumeItem{
Final-year Computer Science undergraduate with strong foundations in Data Structures, Operating Systems, and Networking. Experienced in designing concurrent, ACID-compliant backend systems and containerized microservices using \textbf{Java, Spring Boot, PostgreSQL, and Docker}.
}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {M. S. Ramaiah Institute of Technology}{Bangalore, India}
    {B.E. in Computer Science Engineering (CGPA: 8.68)}{2022 - 2026}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Full Stack Developer Intern}{Bangalore, India}
    {Ramaiah Institute of Technology}{}
    \resumeItemListStart
    \resumeItem{Engineered a MERN-based booking system by implementing JWT-based RBAC and atomic slot validation logic, eliminating 100\% double-booking across 5,000+ simulated reservations.}
    \resumeItem{Improved database performance by introducing indexed MongoDB queries and benchmarking execution paths, increasing retrieval speed by 3x over 5k+ records.}
    \resumeItem{Accelerated release cycles by automating CI pipelines using GitHub Actions, reducing deployment time by 60\% (20 min → 8 min).}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
  {\textbf{Fintech Ledger \& Payments API Platform}
  \href{https://github.com/aryankumar4848/fintech-ledger}{\faIcon{external-link-alt}}
  $|$ \emph{Java, Spring Boot, PostgreSQL}}{}
  \resumeItemListStart
    \resumeItem{Built an ACID-compliant ledger API by implementing transaction isolation and row-level locking, ensuring 100\% consistency across deposit, withdrawal, and transfer operations.}
    \resumeItem{Eliminated duplicate financial transactions by designing idempotency-key validation, maintaining 0\% duplication across 1,000+ concurrent requests.}
    \resumeItem{Optimized API throughput using cursor-based pagination and query tuning, reducing response payload size by 90\% under load testing.}
  \resumeItemListEnd

   \resumeProjectHeading
    {\textbf{Microservice-based Event Booking System}
    \href{https://github.com/aryankumar4848/event-driven-ticket-booking-microservice}{\faIcon{external-link-alt}}
    $|$ \emph{Spring Boot, PostgreSQL, Docker}}{}
    \resumeItemListStart
    \resumeItem{Designed a 3-service microservices architecture (User, Event, Booking) enabling modular deployment and service isolation.}
    \resumeItem{Prevented 100\% seat double-booking under concurrency using transactional database locking and consistency checks.}
    \resumeItem{Validated system scalability using JMeter with 150+ concurrent users, maintaining stable response latency and zero booking conflicts.}
    \resumeItemListEnd

  \resumeProjectHeading
{\textbf{MBTI Cognitive Chatbot (AI Personality Inference System)}
\href{https://github.com/aryankumar4848/mbti-chatbot}{\faIcon{external-link-alt}}
$|$ \emph{React, Node.js, Python, Docker}}{}
\resumeItemListStart
\resumeItem{Built a full-stack AI chatbot by integrating a React frontend, Node.js backend, and Python ML inference service for real-time personality-aware conversations.}
\resumeItem{Deployed an mBERT-based MBTI classifier (16 classes) achieving 0.81 validation AUC across multilingual datasets using TensorFlow SavedModel.}
\resumeItem{Improved conversational relevance by integrating transformer-based emotion detection for sentiment-aware response adaptation.}
\resumeItem{Containerized client, server, and ML services using Docker Compose, enabling modular orchestration and scalable deployment.}
\resumeItemListEnd

  \resumeProjectHeading
    {\textbf{AgriConnect: AI-Powered Agricultural Marketplace \& Advisory Platform}
    \href{https://github.com/aryankumar4848/AgriConnect}{\faIcon{external-link-alt}}
    $|$ \emph{React, Node.js/Express, MongoDB, Razorpay, Docker, Prometheus}}{}
    \resumeItemListStart
      \resumeItem{Developed full-stack e-commerce platform for 40+ agricultural products (seeds, fertilizers) with Razorpay integration, achieving 100\% payment verification across 500+ simulated transactions.}
      \resumeItem{Implemented AI-driven crop recommendation engine using image analysis and soil data, delivering personalized suggestions for 15+ crops with 95\% user satisfaction in beta testing.}
      \resumeItem{Orchestrated monitoring stack with Prometheus, Filebeat, and Logstash, reducing MTTR by 75\% (from 20min to 5min) during load tests with 200+ concurrent users.}
      \resumeItem{Engineered containerized deployment (client + server Dockerfiles), enabling one-command orchestration via docker-compose and zero-downtime updates.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItem{
\textbf{Languages:} Java, Python, JavaScript, SQL \\
\textbf{Backend:} Spring Boot, Spring Cloud, Node.js, REST APIs, Hibernate \\
\textbf{Databases:} PostgreSQL, MySQL, MongoDB \\
\textbf{DevOps:} Docker, Git, GitHub Actions, Jenkins (basic) \\
\textbf{Core Concepts:} DSA, OOPS, Concurrency, Microservices, Distributed Systems \\
\textbf{OS \& Networking:} Process Management, Synchronization, TCP/IP, HTTP/HTTPS
}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS AND ACHIEVEMENTS-----------
\section{Certifications And Achievements}
\resumeSubHeadingListStart

\resumeItem{
\textbf{Research Paper Accepted (IEEE I3CTCON 2026)} — \textit{MBTI Cognitive Chatbot: Personality-Aware Conversational AI Architecture}. 
Accepted for presentation at the IEEE International Conference for Convergence in Computing Technology (I3CTCON), Pune, India. Publication in IEEE Xplore pending.
}

\resumeItem{
\textbf{Azure AZ-900} — In Progress
}

\resumeItem{
\textbf{Solved 200+ DSA Problems} across LeetCode and GeeksforGeeks
}

\resumeSubHeadingListEnd

\end{document}

